---
title: "Expert Evaluations: Round 2"
author: "T. Eerola and C. Kirts"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

This analysis details the Round 2 of the expert ratings. 

```{r}
#| echo: true
#| warning: false
#| id: setup
rm(list=ls())  # clear memory
library(tidyverse) 
library(stringr)
library(psychometric)
library(ggplot2)
library(CVI)
#packageVersion("CVI") # Should be 0.1.4.0 at least

source('scr/read_episode_data_round2.R') # requires ToDo! 
source('scr/preprocess_qualtrics_round2.R') # Not Finished, Complete
source('scr/analyse_episode_data_round2.R') # Not tested
source('scr/add_constructs_round2.R') #Needs work

# write the data to file (as an option)
file_write <- FALSE
```

## Read and preprocess the data

```{r}
#| echo: true
#| id: read-data
#| format: asis
Item_CodeBook <- read.csv("data/Task2_Items_302.csv",header = TRUE)
FC2  <- read_episode_data_round2("data/DEEM2ndFC_March162025.csv")
LMA2 <- read_episode_data_round2("data/DEEM2ndLMA_March162025.csv")
MM2 <- read_episode_data_round2("data/DEEM2ndMM_March162025.csv")

# there is one ID_Code left empty, let's fix it first

FC2$ID_Code.[FC2$ID_Code.==""] <- "XXX"
LMA2$ID_Code.[LMA2$ID_Code.==""] <- c("XXX","SJYU")
MM2$ID_Code.[MM2$ID_Code.==""] <- c("XXX","YYY")

#table(FC2$ID_Code.) # One duplicate, EDU, remove the first take
dupl_index <- which(FC2$ID_Code.=="EDU")[1]
FC2 <- FC2[-dupl_index,] # delete the duplicated response

# diagnose who were the missing experts
#table(LMA2$ID_Code.)
#table(MM2$ID_Code.)
#table(FC2$ID_Code.)
#length(table(FC2$ID_Code.))

# check whether XXX and YYY are test responses (or partial responses)
#tmp1<-FC2[,FC2$ID_Code.=="AMU"]
#tmp2<-FC2[,FC2$ID_Code.=="XXX"]
#tmp3<-MM2[,MM2$ID_Code.=="YYY"]

# YYY seems to be a genuine but lone response, let's remove it for now
dupl_index <- which(MM2$ID_Code.=="YYY")[1]
MM2 <- MM2[-dupl_index,] # delete the duplicated response

# Now we have 14 experts across all three constructs

# this function does not bring the ranking data at all, let's fix it.
FC2B <- preprocess_qualtrics_round2(FC2) # FC2<-FC2$rating not populating spreadsheet properly
LMA2B <- preprocess_qualtrics_round2(LMA2)
MM2B <- preprocess_qualtrics_round2(MM2)

```

## Define constructs and merge into a data frame

```{r}
#| echo: true
#| id: define-constructs
#| result: asis

FC2_constructs <- add_constructs_round2(FC2B$rating,'FC2')
LMA2_constructs <- add_constructs_round2(LMA2B$rating,'LMA2')
MM2_constructs <- add_constructs_round2(MM2B$rating, 'MM2')

DF <- rbind(FC2_constructs,LMA2_constructs,MM2_constructs)
#table(DF$construct)                # just checking, all OK
#print(knitr::kable(table(DF$construct,DF$ID_Code.)))    # just checking, all OK
```

Summarise what we have (no of ratings across constructs and experts)

```{r}
#| format: asis
#| echo: true
#| id: summary
#knitr::kable(table(DF$construct,DF$IDCode))
#length(unique(DF$ID_Code.)) # number of experts

DF$ID_Code. <- factor(DF$ID_Code.,labels = paste0('Ex',sprintf('%0.2d',1:length(unique(DF$ID_Code.)))))
knitr::kable(table(DF$construct,DF$ID_Code.))

```

Add actual items to the data frame from the codebook.

```{r}
#| id: Item-Codebook
#| eval: false
#### CHECK in progress
U_codebook <- unique(Item_CodeBook$Rele_ID)
U_data <- unique(FC2B$rating$name)
U_data2 <- unique(MM2B$rating$name)
U_data3 <- unique(LMA2B$rating$name)
U_comb <- unique(c(U_data,U_data2,U_data3))
length(U_comb) # 302

m <- U_codebook %in% U_comb
sum(m) # 302, correct!
FC2B$rating$item_text <- Item_CodeBook$Item[match(FC2B$rating$name,Item_CodeBook$Rele_ID)]

```


## Calculate Content Validity

Here we use the CVI package. In the analysis of the items in stage one, we rely on CVI (adjusted) and the same for the figures.

```{r}
#| id: Calculate-CVI
# Calculate CVI for each construct 
Constructs <- unique(DF$construct)
Items<-list()
Items_trimmed <- list()
Scales_full <- list()
Scales_trimmed <- list()
Item_N <- NULL
Item_N_trimmed <- NULL
for (i in 1:length(Constructs)){
  Items[[i]] <- CVI_item(DF[DF$construct==Constructs[i],2:4])
  Item_N[i] <- nrow(Items[[i]])
  Items_trimmed[[i]] <- Items[[i]][Items[[i]]$CVIFit=='Appropriate',]
  Item_N_trimmed[i] <- nrow(Items_trimmed[[i]])
  Scales_full[[i]] <- CVI_scale(Items[[i]])  
  Scales_trimmed[[i]] <- CVI_scale(Items_trimmed[[i]])  
}
Construct_table <- data.frame(Constructs = Constructs, 
                             Item_n = Item_N,
                             SCVI_Ave = unlist(Scales_full),
                             Item_n_T = Item_N_trimmed,
                             SCVI_AveT = unlist(Scales_trimmed)
)
knitr::kable(Construct_table,digits=2)
```

## Visualise constructs

```{r}
#| echo: false
#| id: visualise
fig <- list()
for (i in 1:length(Constructs)){
  Items[[i]]<-CVI_item(DF[DF$construct==Constructs[i],2:4])
  fig[[i]] <- CVI_visualise(Items[[i]],showlegend = TRUE,colorvar = 'CVIFit') # default CVI.I.adj and Kappa
  fig[[i]] <- fig[[i]] + ggtitle(Constructs[i])
}  

Categories <- NULL
Categories$FC2 <- c('EDR','FM','CB','AIA','PEP')
Categories$EDR <- c('Enjoyment','Distraction','Relaxation')
Categories$CB <- c('Connection','Belonging')
Categories$FM <- c('Energy Control','Focus')
Categories$PEP <- c('Coping','Feeling')
Categories$AIA <- c('Moved','Curiosity','Aesthetics')
Categories$LMA2 <- c('Diffuse','Bodily','Emotional','Associative','Structural','Reduced')
Categories$MM2 <- c('Structure', 'Self', 'Source')
Categories$QRE <- c('Qualia','Preference & Familiarity')

```


### Enjoyment-Distraction-Relaxation

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5
#| id: EDR 
index <- Constructs %in% Categories$EDR
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$EDR[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$EDR[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$EDR[3])
```

### Connection-Belonging

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5
#| id: CB 
index <- Constructs %in% Categories$CB
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$CB[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$CB[2])
```


### Focus-Motivation

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: FM
index <- Constructs %in% Categories$FM
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$FM[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$FM[2])
```


### Personal Emotional Processing

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: PEP
index <- Constructs %in% Categories$PEP
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$PEP[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$PEP[2])
```


### Aesthetic–Interest–Awe 

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 10.5 
#| id: AIA
index <- Constructs %in% Categories$AIA
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$AIA[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$AIA[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$AIA[3])
```


### Listening Modes and Agency

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 18 
#| id: LMA
index <- Constructs %in% Categories$LMA
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],fig[[which(index)[4]]],fig[[which(index)[5]]],ncol=1,nrow=5)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$LMA[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$LMA[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$LMA[3])
knitr::kable(Items[[which(index)[4]]],digits=2,caption = Categories$LMA[4])
knitr::kable(Items[[which(index)[5]]],digits=2,caption = Categories$LMA[5])
```

### Musical Meanings

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 10.5 
#| id: MM
index <- Constructs %in% Categories$MM
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$MM[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$MM[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$MM[3])
```

### Qualia, Reward and Exposure

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: QRE
index <- Constructs %in% Categories$QRE
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$QRE[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$QRE[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$QRE[3])
```




```{r}
#| echo: false

if(file_write == TRUE){
 save(DF,file = 'All_Item_data_R2.Rdata')
 save(Constructs,file = 'Constructs_R2.Rdata')
}
```


