---
title: "Expert Evaluations: Round 1"
author: "T. Eerola and C. Kirts"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
---

This analysis details the Round 1 of the expert ratings. The data consist of ratings of 329 items across 24 constructs rated by 14 experts. 

```{r}
#| echo: true
#| warning: false
#| id: setup
rm(list=ls())  # clear memory
library(tidyverse) 
library(stringr)
library(psychometric)
library(ggplot2)
library(CVI)
#packageVersion("CVI") # Should be 0.1.4.0 at least

source('scr/read_episode_data.R') # requires ToDo! 
source('scr/preprocess_qualtrics.R') # Not Finished, Complete
source('scr/analyse_episode_data.R') # Not tested
source('scr/add_constructs.R') #Needs work

# write the data to file (as an option)
file_write <- FALSE
```

## Read and preprocess the data

```{r}
#| echo: true
#| format: asis
#| id: read-data
FM  <- read_episode_data("data/FM_October312024.csv")
CB  <- read_episode_data("data/CB_October312024.csv")
EDR <- read_episode_data("data/EDR_October312024.csv")
AIA <- read_episode_data("data/AIA_October312024.csv")
PEP <- read_episode_data("data/PEP_October312024.csv")
LMA <- read_episode_data("data/LMA_October312024.csv")
MM  <- read_episode_data("data/MM_October312024.csv")
QRE <- read_episode_data("data/QRE_October312024.csv")

FM <- preprocess_qualtrics(FM) 
CB <- preprocess_qualtrics(CB)
EDR <- preprocess_qualtrics(EDR)
AIA <- preprocess_qualtrics(AIA)
PEP <- preprocess_qualtrics(PEP)
LMA <- preprocess_qualtrics(LMA)
MM <- preprocess_qualtrics(MM)
QRE <- preprocess_qualtrics(QRE)

#source('scr/coder_initials.R') # Anonymise the experts in the end
 
```

### Define constructs and merge into a data frame

```{r}
#| echo: true
#| id: definitions
FM_constructs <- add_constructs(FM$rating,'FM')
CB_constructs <- add_constructs(CB$rating,'CB')
EDR_constructs <- add_constructs(EDR$rating,'EDR')
AIA_constructs <- add_constructs(AIA$rating,'AIA')
PEP_constructs <- add_constructs(PEP$rating,'PEP')
LMA_constructs <- add_constructs(LMA$rating,'LMA')
MM_constructs <- add_constructs(MM$rating,'MM')
QRE_constructs <- add_constructs(QRE$rating,'QRE')

# combine all constructs to a single data frame
DF <- rbind(FM_constructs,
            CB_constructs,
            EDR_constructs,
            AIA_constructs,
            PEP_constructs,
            LMA_constructs,
            MM_constructs,
            QRE_constructs)

DF$IDCode[DF$IDCode==""]<-"Unknown" # replace empty IDCode with "Unknown
```

### Summarise the observations

Show the number of ratings across constructs and experts. As we can observe, we have some minor gaps in the data as not all the experts have completed the ratings for all the constructs.

```{r}
#| format: asis
#| echo: true
#| id: summarise
#knitr::kable(table(DF$construct,DF$IDCode))
DF <- dplyr::filter(DF,IDCode!="Unknown") # remove IDCode = Unknown
DF <- dplyr::filter(DF,IDCode!="KDU") # remove IDCode = KDU
# remove double coded expert at coder_initials,R
# length(unique(DF$IDCode)) # number of experts

DF$IDCode <- factor(DF$IDCode,labels = paste0('Ex',sprintf('%0.2d',1:length(unique(DF$IDCode)))))
knitr::kable(table(DF$construct,DF$IDCode))

# rename RC to CC in Coping
library(stringr)
DF$name[DF$construct=='Coping']<-str_replace(DF$name[DF$construct=='Coping'],'RC','CC')
#knitr::kable(table(DF$name,DF$construct))
```

## Calculate Content Validity

Here we use the [CVI package](https://github.com/tuomaseerola/CVI). In the analysis of the items in Round 1, we rely on CVI (adjusted) and the same for the figures.

```{r}
#| id: Calculate-CVI
# Calculate CVI for each construct 
Constructs <- unique(DF$construct)
Items<-list()
Items_trimmed <- list()
Scales_full <- list()
Scales_trimmed <- list()
Item_N <- NULL
Item_N_trimmed <- NULL
for (i in 1:length(Constructs)){
  Items[[i]] <- CVI_item(DF[DF$construct==Constructs[i],2:4])
  Item_N[i] <- nrow(Items[[i]])
  Items_trimmed[[i]] <- Items[[i]][Items[[i]]$CVIFit=='Appropriate',]
  Item_N_trimmed[i] <- nrow(Items_trimmed[[i]])
  Scales_full[[i]] <- CVI_scale(Items[[i]])  
  Scales_trimmed[[i]] <- CVI_scale(Items_trimmed[[i]])  
}
Construct_table <- data.frame(Constructs = Constructs, 
                             Item_n = Item_N,
                             SCVI_Ave = unlist(Scales_full),
                             Item_n_T = Item_N_trimmed,
                             SCVI_AveT = unlist(Scales_trimmed)
)
knitr::kable(Construct_table,digits=2)
```

## Visualise item relevance across constructs and sub-constructs

```{r}
#| echo: false
#| id: visualise
fig <- list()
for (i in 1:length(Constructs)){
  Items[[i]]<-CVI_item(DF[DF$construct==Constructs[i],2:4])
  fig[[i]] <- CVI_visualise(Items[[i]],showlegend = TRUE,colorvar = 'CVIFit') # default CVI.I.adj and Kappa
  fig[[i]] <- fig[[i]] + ggtitle(Constructs[i])
}
# define categories
Categories <- NULL
Categories$EDR <- c('Enjoyment','Distraction','Relaxation')
Categories$CB <- c('Connection','Belonging')
Categories$FM <- c('Energy','Focus')
Categories$PEP <- c('Coping', 'Feeling')
Categories$AIA <- c('Moved', 'Curiosity','Aesthetics')
Categories$LMA <- c('Diffuse','Bodily','Emotional','Associative','Structural','Reduced')
Categories$MM <- c('Structure', 'Self', 'Source')
Categories$QRE <- c('Qualia','Preference','Familiar')
```

### Enjoyment-Distraction-Relaxation

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5
#| id: EDR 
index <- Constructs %in% Categories$EDR
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$EDR[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$EDR[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$EDR[3])
```

### Connection-Belonging

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5
#| id: CB 
index <- Constructs %in% Categories$CB
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$CB[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$CB[2])
```


### Focus-Motivation

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: FM
index <- Constructs %in% Categories$FM
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$FM[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$FM[2])
```


### Personal Emotional Processing

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: PEP
index <- Constructs %in% Categories$PEP
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],ncol=1,nrow=2)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$PEP[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$PEP[2])
```


### Aesthetic–Interest–Awe 

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 10.5 
#| id: AIA
index <- Constructs %in% Categories$AIA
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$AIA[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$AIA[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$AIA[3])
```


### Listening Modes and Agency

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 18 
#| id: LMA
index <- Constructs %in% Categories$LMA
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],fig[[which(index)[4]]],fig[[which(index)[5]]],ncol=1,nrow=5)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$LMA[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$LMA[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$LMA[3])
knitr::kable(Items[[which(index)[4]]],digits=2,caption = Categories$LMA[4])
knitr::kable(Items[[which(index)[5]]],digits=2,caption = Categories$LMA[5])
```

### Musical Meanings

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 10.5 
#| id: MM
index <- Constructs %in% Categories$MM
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$MM[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$MM[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$MM[3])
```

### Qualia, Reward and Exposure

```{r}
#| echo: false
#| fig.width: 7
#| fig.height: 7.5 
#| id: QRE
index <- Constructs %in% Categories$QRE
cowplot::plot_grid(fig[[which(index)[1]]],fig[[which(index)[2]]],fig[[which(index)[3]]],ncol=1,nrow=3)
knitr::kable(Items[[which(index)[1]]],digits=2,caption = Categories$QRE[1])
knitr::kable(Items[[which(index)[2]]],digits=2,caption = Categories$QRE[2])
knitr::kable(Items[[which(index)[3]]],digits=2,caption = Categories$QRE[3])
```

See [item_decisions](item_decisions.qmd) for full details.


```{r}
#| echo: false
#| id: save-data
# Save data if needed
if(file_write == TRUE){
 save(DF,file = 'All_Item_data.Rdata')
 save(Constructs,file = 'Constructs.Rdata')
}
```
